Using the internal language of toposes in algebraic geometry

### 2014-06-18 poster.tex
Further keywords

  \vspace{1cm}
  \begin{alertblock}{Dictionary of external vs. internal notions}
    Expository notes are available at \url{http://tiny.cc/topos} (work in
    progress).
  \end{alertblock}
\end{column}

@@

* term "intuitionistic"
* more examples, other toposes, ...
* further work
* own contributions
* "at once"
* orphans
* blue borders in alertboxes

>>>>

  \vspace{1cm}
  \begin{alertblock}{Dictionary of external vs. internal notions}
    Expository notes are available at \url{http://tiny.cc/topos} (work in
    progress).
  \end{alertblock}
  \tiny\rmfamily\justifying
  Tensor product of sheaves $=$ internal ordinary tensor product,
  internal Cartier divisors,
  quasicoherent sheaves $=$ internal ordinary modules satisfying an interesting
  condition,
  more metatheorems about spreading of properties,
  pullback along immersions $=$ internal sheafification,
  relative spectrum $=$ internal spectrum,
  scheme dimension $=$ Krull dimension of~$\O_X$,
  dense $=$ not not,
  further modal operators,
  other toposes,
  group schemes $=$ groups,
  \ldots
\end{column}

@@

* own contributions
* "at once"
